Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2021-02-23 inst/manuscript/manuscript.Rmd
Merge in Su's edits to manuscript and SI

<!-- values. The first is based on a simplified formula of the Haze Optimized Transformation (HOT) index [@Zhangimagetransformcharacterize2002; @ZhuObjectbasedcloudcloud2012]:  -->

@@

\begin{equation} \label{eq:shadow}  
\mathrm{W2_t} =\begin{cases}
    1, & \text{if $\mathrm{NIR_t}$ < median\{$\mathrm{NIR_1}$, $\mathrm{NIR_2}$, ..., $\mathrm{NIR_i}$\}}.\\
    \frac{1}{\mathrm{NIR_t}^4}, & \text{otherwise}.
  \end{cases}
\end{equation}

Where *t* is a particular date in near-daily time series of PlanetScope images, which begins at date 1 for the given compositing period and ends on date *i*, *blue* is the blue band, and *NIR* the near infrared band. Equation \ref{eq:cloud} assigns lower weights to hazy and clouded pixels, while equation \ref{eq:shadow} assigns low weights to pixels in cloud shadow.

@@

\begin{equation}
\mathrm{score_i}=\beta0\mathrm{I}+\beta1\mathrm{O}+\beta2\mathrm{F}+\beta3\mathrm{E}+\beta4\mathrm{C}
\end{equation}

@@

In the second step, a Sobel filter is then applied to the green, red, and near-infrared mean-shifted bands [**I assume**], and weighted edge image is computed using weights of 1, 1, and 2 to each band for the dry season only [**or growing season?**]. A watershed algorithm (**cite**) is then run on the weighted edge image, with a high level of segmentation specified. In this case, we specified **2400** segments per tile.

In the third step, a region adjacency graph is constructed for each tile, in which each node represents all pixels within each polygon created in the previous step. The edge between two adjacent regions (polygons) is calculated as the difference between the means of normalized colors of all bands. Hierarchical merging is then applied, in which the most similar pairs of adjacent nodes are merged until there are no edges remaining below a predetermined threshold of **X**.

@@

In the final step, the retained polygons are refined by removing holes and smoothing their boundaries using the Douglas-Peucker algorithm (cite). Neighboring polygon that touch along tile boundaries are merged.

To assess the accuracy of the final segmented boundaries, we used a two-step approach. First, we assessed the overall thematic accuracy of the resulting classification against our map reference data. Second, to assess the quality of the segmentation, we compared the mean area and relative frequencies of the segmented polygons within different size classes against the same metrics derived from the digitized fields of the most accurate worker to create the given map. [**Note: the following maybe better for discussion**] We selected this relatively simple procedure, as opposed to more complex measures of object accuracy (**cite**), because, on the one hand, both the automated segmentation algorithm and human interpreter are cueing in on the same features--abrupt, physically detectable breaks within the imagery. On the other hand, no matter how well the intepreted/segmented boundaries align with the boundaries of fields in the imagery, it is logistically difficult and potentially impossible to evaluate performance against the boundaries that farmers use to delineate their fields, as the conception of a "field" may vary between farmers (**cite**) and their field edges may be invisible or span multiple units that appear to a segmentation to have distinct boundaries (**see SI**).

@@

# Discussion
We present here a method for developing high resolution maps that detail the characteristics of smallholder-dominated croplands, providing information on their geometries and distribution of <5 m resolution, and representing a single agricultural year.

>>>>

<!-- values. The first is based on a simplified formula of the Haze Optimized Transformation (HOT) index [√; @ZhuObjectbasedcloudcloud2012]:  -->

@@

\begin{equation} \label{eq:shadow}  
\mathrm{W2_t} =\begin{cases}
    \frac{1}{\mathrm{NIR_t}^4}, & \text{if $\mathrm{NIR_t}$ < median\{$\mathrm{NIR_1}$, $\mathrm{NIR_2}$, ..., $\mathrm{NIR_i}$\}}.\\
    1, & \text{otherwise}.
  \end{cases}
\end{equation}

Where *t* is a particular date in near-daily time series of PlanetScope images, which begins at date 1 for the given compositing period and ends on date *i*, *blue* is the blue band, and *NIR* the near infrared band.Equation \ref{eq:cloud} assigns lower weights to hazy and clouded pixels as the blue band is sensitive to haze and cloud pixels [@Zhangimagetransformcharacterize2002], while equation \ref{eq:shadow} assigns low weights to pixels in cloud shadow considering the significant darkening effect of the cloud shadows in the Near Infrared band [@ZhuObjectbasedcloudcloud2012; @ShiCirrusCloudsThatAffect2020].

@@

\begin{equation}
\mathrm{score_i}=\beta_0\mathrm{I}+\beta_1\mathrm{O}+\beta_2\mathrm{F}+\beta_3\mathrm{E}+\beta_4\mathrm{C}
\end{equation}

@@

In the second step, a Sobel filter is then applied to the green, red, near-infrared mean-shifted bands and probability map , and an combined edge image is computed using the sum of these four edge images for the dry season only. A compact watershed algorithm [@NeubertCompactWatershedPreemptiveSlic2014] is then run on the weighted edge image, with a high level of segmentation specified. In this case, we specified **6400** segments per tile.

In the third step, a region adjacency graph is constructed for each tile, in which each node represents all pixels within each polygon created in the previous step. The edge between two adjacent regions (polygons) is calculated as the norm of the difference between the means of normalized colors of all bands. Hierarchical merging is then applied, in which the most similar pairs of adjacent nodes are merged until there are no edges remaining below a predetermined threshold of 0.05.

@@

In the final step, the retained polygons are refined by removing holes and smoothing their boundaries using the Visvalingam algorithm [@VisvalingamLineGeneralisation1993]. Neighboring polygon that touch along tile boundaries are merged.

To assess the accuracy of the final segmented boundaries, we used a two-step approach. First, we assessed the overall thematic accuracy of the resulting classification against our map reference data. Second, to assess the quality of the segmentation, we compared the mean area and relative frequencies of the segmented polygons within different size classes against the same metrics derived from the digitized fields of the most accurate worker to create the given map. [**Note: the following maybe better for discussion**] We selected this relatively simple procedure, as opposed to more complex measures of object accuracy [@YeReviewAccuracyAssessment2018], because, on the one hand, both the automated segmentation algorithm and human interpreter are cueing in on the same features--abrupt, physically detectable breaks within the imagery. On the other hand, no matter how well the intepreted/segmented boundaries align with the boundaries of fields in the imagery, it is logistically difficult and potentially impossible to evaluate performance against the boundaries that farmers use to delineate their fields, as the conception of a "field" may vary between farmers (**cite**) and their field edges may be invisible or span multiple units that appear to a segmentation to have distinct boundaries (**see SI**).

@@

# Discussion

We present here a method for developing high resolution maps that detail the characteristics of smallholder-dominated croplands, providing information on their geometries and distribution of <5 m resolution, and representing a single agricultural year.

### 2021-02-23 inst/manuscript/si.Rmd
Merge in Su's edits to manuscript and SI

After creating the consensus label, the degree of confidence in the resulting label value is measured by Bayes Risk:

@@

Using equation \ref{eq:pixelrisk}, the corresponding risk associated with this particular pixel's label is thus `r rj * (1 - 1) + (1 - rj) * 1`.

@@

>>>>

After creating the consensus label, the degree of confidence in the resulting label value is measured by Bayesian Risk:

@@

Using equation \ref{eq:pixelrisk}, the corresponding risk associated with this particular pixel's label is thus `r rj * (1 - 1) + (1 - rj) * 1` (i.e., 1 - `r rj <- round((wtA * 1 + wtB * 0) / (wtA + wtB), 3); rj`).

@@

#### Worker's assignment evaluation
We assigned a score for each workers' assign; the score history determines the weights of each workers for creating a consensus label for each 0.005 degree resolution grid. The score for a particular assignment *i* is defined as a weighted sum of five accuracy metrics:
$$ score_i=\beta_0\mathrm{I}+\beta_1\mathrm{O}+\beta_2\mathrm{F}+\beta_3\mathrm{E}+\beta_4\mathrm{C}$$
Where $\beta_{0-5}$ are the weights assigned to each accuracy metric that sum to 1. For the current production version, $\beta_{0-5}$ were assigned as 0.4, 0.2, 0.2, 0.1, and 0.1.
*I* is "inside the box" accuracy which is defined as a proportion of the area correctly mapped within a 0.005 degree resolution grid (*I_c*) over total "inside the box" area for this grid (*I_t*).
$$ I=\frac{I_c}{I_t}$$
*O* is "outside the box" accuracy which refers to a proportion of the field area correctly mapped outside the grid over total "outside the box" region (*O_t*, the region within the bounding box of the workers' polygons but not within 0.005 degree resolution grid).
$$ O=\frac{O_c}{O_t}$$
*F* is the fragmentation accuracy which is defined as a proportion of matched polygon number (*N_m*, the number of the workers' polygons that has at least 50% of its region overlapped with a reference polygon) over total workers' polygon number (*N_t*).
$$ F=\frac{N_m}{N_t}$$
*E* is the average edge accuracy for all pairs of matched workers and refernece polygons; the edge accuracy for a single pair is defined as the length of 'correctly mapped edges' (*L_c*, the partial boundary of a workers' polygon that are within a three-planet-pixel buffer region of the matched reference polygon boundary) over the total boundary length of its matched reference polygon (*L_t*). 
$$ E=\frac{L_c}{L_t}$$
*C* is the categorical accuracy, i.e., a proportion of the area that has been correctly labeled with field category within intersected regions between worker's and reference polygons (*T_c*) over the total intersecting area (*T_t*).
$$ C=\frac{T_c}{T_t}$$
